RESEARCH PROPOSAL

### 2022-05-24 papers/fuzzy-fmt/OralExm-researchproposal.tex
oralexm edits

In selecting a soft interatomic potential to use as a reference fluid, 
there is one choice to consider that stands out above others, and that is 
the repulsive portion of the interatomic potential of the 
Weeks-Chandler-Andersen (WCA) fluid.
The WCA potential reproduces the repulsive force of the Lennard-Jones 
interatomic potential that is used to model neutral atoms. 
The thermodynamic properties of the fluid can be obtained from the 
Helmholtz free energy which
can be expressed as a functional of the average number 
density profile $n(\vec r)$ 
which gives the probability of finding a particle at each position $\vec r$. 
The Helmholtz free energy, along with the corresponding equilibrium number density profile,
can be found using density functional theory by 
varying the number density profile until the free energy is minimized.
For classical fluids, Rosenfeld formulated a highly successful 
density functional theory called Fundamental Measure Theory (FMT)
by noting that the Mayer function of the hard-sphere fluid is a step function
that can be decomposed into a set of weight functions that can be used 
to express the Helmholtz free energy functional in terms of a set of weighted densities. 
Schmidt created Soft Fundamental Measure Theory (SFMT) for soft sphere 
fluids which is based on FMT but reformulated for soft potentials by 
meeting the limiting conditions for a 0-dimensional fluid (where a sphere 
is confined to a cavity large enough for only one sphere) 
and for low-density. 
Emerging from his work is an "error-function" potential he formed to 
demonstrate the application of SFMT to a soft-sphere fluid and which is
similar to the repulsive potential of the WCA fluid. However, 
Schmidt's error function potential can only be made similar to the WCA fluid 
at one temperature -
it will not work for a variety of temperatures. 
Therefore, we use the error function potential but make
its parameters temperature-dependent (similar to the way Barker-Henderson made the
diameter of the hard sphere fluid temperature-dependent).
One parameter makes the softness of the error function potential comparable 
with the softness (steepness) of the WCA potential, while the other parameter 
sets the length-scale of the particle interaction and
is derived by 
setting the second virial coefficient of our error function potential equal to the second virial 
coefficient of a WCA fluid. 
Our approach is easily extensible to other soft repulsive potentials.

>>>>

In selecting a soft interatomic potential to use as a reference fluid, 
there is one choice to consider that stands out above others, and that is 
the repulsive portion of the interatomic potential of the 
Weeks-Chandler-Andersen (WCA) fluid.
The WCA potential reproduces the repulsive force of the Lennard-Jones 
interatomic potential that is used to model neutral atoms. 
The thermodynamic properties of the fluid can be obtained from the 
Helmholtz free energy which
can be expressed as a functional of the average number 
density profile $n(\vec r)$ 
which gives the probability of finding a particle at each position $\vec r$. 
The Helmholtz free energy, along with the corresponding equilibrium number density profile,
can be found using density functional theory by 
varying the number density profile until the free energy is minimized.
For classical fluids, Rosenfeld formulated a highly successful 
density functional theory called Fundamental Measure Theory (FMT)
by noting that the Mayer function of the hard-sphere fluid is a step function
that can be decomposed into a set of weight functions that can be used 
to express the Helmholtz free energy functional in terms of a set of weighted densities. 
Schmidt created Soft Fundamental Measure Theory (SFMT) for soft sphere 
fluids which is based on FMT but reformulated for soft potentials by 
meeting the limiting conditions for a 0-dimensional fluid (where a sphere 
is confined to a cavity large enough for only one sphere) 
and for low-density. 
Emerging from his work is an "error-function" potential he formed to 
demonstrate the application of SFMT to a soft-sphere fluid and which is
similar to the repulsive potential of the WCA fluid. However, 
Schmidt's error function potential can only be made similar to the WCA fluid 
at one temperature -
it will not work for a variety of temperatures. 
Therefore, we use the error function potential but make
its parameters temperature-dependent (similar to the way Barker-Henderson made the
diameter of the hard sphere fluid temperature-dependent). 
%One parameter makes the softness of the error function potential comparable 
%with the softness (steepness) of the WCA potential, while the other parameter 
%sets the length-scale of the particle interaction and is
%derived by setting 
%We design the parameters make
Our parameters are derived in part by making 
the second virial coefficient of our error function 
potential equal to the second virial coefficient of a WCA fluid. 
Our approach is easily extensible to other soft repulsive potentials.
